An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-06-15 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

Optimization of PV systems is not a recent topic; since the $90$'s different techniques 
using a wide variety of criteria to find ultimate combinations for design parameters, 
based on intuitive, numerical and analytical methods were developed and evaluated \textcolor{red}{add citation}. 
An ideal combination of any PV system is made by the best compromise between 
two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.

@@

During the PV system design, one of the most important aspects to ensure power system reliability 
is to analyze power supply availability \textcolor{red}{add citation here}. The reason is because solar 
energy production is intermittent and, therefore, the energy generated usually will not match 
with the load demand. A reliable power is a generation system that has sufficient power 
to feed load demand in a period.

@@

NPC is the total present value of a time series. \textcolor{red}{this sentence is unclear or maybe I'm not familiar with this term... 
The net present worth is found by discounting all cash inflows and outflows}, 
including cost of installation, replacement and maintenance of the PV system, 
at an interest rate of internal rate of return (IRR)~\cite{Park2004}.

>>>>

Optimization of PV systems is not a recent topic; since the $90$'s different techniques 
using a wide variety of criteria to find ultimate combinations for design parameters, 
based on intuitive, numerical and analytical methods were developed and evaluated \textcolor{red}{~\cite{Applasamy2011}}. 
An ideal combination of any PV system is made by the best compromise between 
two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.

@@

During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability \textcolor{red}{~\cite{Alsadi2018}}. The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand. A reliable power is a generation system that has sufficient power to feed load demand in a period.

@@

\textcolor{red}{The NPC or life-cycle cost is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime. The net present worth is found by discounting all cash inflows and outflows}, 
including cost of installation, replacement and maintenance of the PV system, 
at an internal rate of return (IRR)~\cite{Park2004}.  IRR is used to evaluate the attractiveness of a project or investment.
